Analysis Stand Features 

### 2018-01-22 analysis/analysis_stand_features.Rmd
update

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:   
  md_document:
    toc: true
    variant: markdown_github
---

@@

@@

site_general <- general_var %>% 
  left_join(coord_sites, by='site') %>% 
  left_join(topo_site, by='site')

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:  pdf_document
bibliography: references.bib 
csl: ecology.csl
---

@@

```{r}
ft_summary <- ft_sel %>% group_by(site) %>% 
  dplyr::summarise(h_mean = mean(h),
                   h_sd = sd(h),
                   dn_mean = mean(dn),
                   dn_sd = sd(dn)) %>% 
  as.data.frame()

compe_summary <- compe %>%  
  mutate(ba_ha = (ba * 10000)/(pi*100)) %>% 
  group_by(site) %>% 
  dplyr::select(ba_ha, std, site) %>% 
  dplyr::summarise(ba_mean = mean(ba_ha), 
                   ba_sd = sd(ba_ha),
                   stand_density_mean = mean(std), 
                   stand_density_sd = sd(std)) %>% 
  as.data.frame()

# DBH and H of all trees (no focal tree)

all <- nft %>% mutate(dn = dn_mm / 10, 
                      h = height_cm / 100) %>% 
  dplyr::select(dn, h, site) %>% 
  bind_rows(ft_sel) %>% 
  group_by(site) %>% 
  dplyr::summarise(h_mean_all = mean(h),
                   h_sd_all = sd(h),
                   dn_mean_all = mean(dn),
                   dn_sd_all = sd(dn)) %>% 
  as.data.frame()

stand_biotic <- ft_summary %>% 
  inner_join(compe_summary, by = 'site') %>% 
  inner_join(all, by='site')

# Export data 
write.csv(stand_biotic, file=paste(di, "data/competence/biotic_stand_features.csv", sep=""), row.names = FALSE)

pander(stand_biotic)
```

@@

site_general <- general_var %>% 
  left_join(coord_sites, by='site') %>% 
  left_join(topo_site, by='site') %>% 
  as.data.frame()

pander(site_general)
